A novel method for detecting coalescing binaries in near realtime with Advanced LIGO and beyond \editorial{Submit to PRD or CQG?}

### 2011-02-15 method.tex
some refinements to svd language
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@621 ccdd05d5-56c1-461a-bf98-85f6876523b4

Our second innovation exploits the fact that the templates in inspiral template banks are, by design, highly correlated.  It is possible to greatly reduce the number of matched filters required to achieve a particular minimum match by designing an appropriate set of orthonormal {\em basis templates}.  A purely numerical technique based on the singular value decomposition (\textsc{svd}) is demonstrated by the authors in~\cite{Cannon:2010p10398}.

>>>>

Our second innovation exploits the fact that the templates in inspiral template banks are, by design, highly correlated.  It is possible to greatly reduce the number of matched filters required to achieve a particular minimum match by designing an appropriate set of orthonormal {\em basis templates}.  A purely numerical technique based on the application of the singular value decomposition (\textsc{svd}) to inspiral waveforms is demonstrated by the authors in~\cite{Cannon:2010p10398}.
